### 2022-04-07 draft.tex
Deploying to gh-pages from @ PoisotLab/ms_betacov_mapping@0380a385b3465bcaad0a778806c03312f02b8a8e 🚀

%
\href{https://orcid.org/0000-0002-0735-5184}{Timothée\,Poisot}%
%
\,\textsuperscript{1,2,‡}\quad %
Peregrin\,Took%
%
\,\textsuperscript{3,4}\quad %
Merriadoc\,Brandybuck%
%
\,\textsuperscript{5,4,‡}

\textsuperscript{1}\,Université de
Montréal\quad \textsuperscript{2}\,Québec Centre for Biodiversity
Sciences\quad \textsuperscript{3}\,Inn of the Prancing
Pony\quad \textsuperscript{4}\,Fellowship of the
Ring\quad \textsuperscript{5}\,Green Dragon Inn

>>>>

%
Norma\,Forero Rocio Munoz%
%
\,\textsuperscript{1,2}\quad %
Renata L.\,Muylaert%
%
\,\textsuperscript{3}\quad %
Stephanie N.\,Seifert%
%
\,\textsuperscript{4}\quad %
Gregory F.\,Albery%
%
\,\textsuperscript{5}\quad %
Colin J.\,Carlson%
%
\,\textsuperscript{5}\quad %
\href{https://orcid.org/0000-0002-0735-5184}{Timothée\,Poisot}%
%
\,\textsuperscript{1,2,‡}

\textsuperscript{1}\,Université de
Montréal\quad \textsuperscript{2}\,Québec Centre for Biodiversity
Sciences\quad \textsuperscript{3}\,Molecular Epidemiology and Public
Health Laboratory, Hopkirk Research Institute, Massey University,
Palmerston North, New Zealand\quad \textsuperscript{4}\,Paul G. Allen
School for Global Health, Washington State University, Pullman, WA,
United States\quad \textsuperscript{5}\,???

### 2022-04-07 preprint.tex
Deploying to gh-pages from @ PoisotLab/ms_betacov_mapping@0380a385b3465bcaad0a778806c03312f02b8a8e 🚀

\medskip
\begin{flushleft}
{\small
%
\href{https://orcid.org/0000-0002-0735-5184}{Timothée\,Poisot}%
%
\,\textsuperscript{1,2,‡}, %
Peregrin\,Took%
%
\,\textsuperscript{3,4}, %
Merriadoc\,Brandybuck%
%
\,\textsuperscript{5,4,‡}
\vskip 1em
\textsuperscript{1}\,Université de Montréal; \textsuperscript{2}\,Québec
Centre for Biodiversity Sciences; \textsuperscript{3}\,Inn of the
Prancing Pony; \textsuperscript{4}\,Fellowship of the
Ring; \textsuperscript{5}\,Green Dragon Inn\\
\textsuperscript{‡}\,These authors contributed equally to the work\\
\vskip 1em
\textbf{Correspondance to:}\\
Timothée Poisot --- \texttt{timothee.poisot@umontreal.ca}\\
}
\end{flushleft}

>>>>

\medskip
\begin{flushleft}
{\small
%
Norma\,Forero Rocio Munoz%
%
\,\textsuperscript{1,2}, %
Renata L.\,Muylaert%
%
\,\textsuperscript{3}, %
Stephanie N.\,Seifert%
%
\,\textsuperscript{4}, %
Gregory F.\,Albery%
%
\,\textsuperscript{5}, %
Colin J.\,Carlson%
%
\,\textsuperscript{5}, %
\href{https://orcid.org/0000-0002-0735-5184}{Timothée\,Poisot}%
%
\,\textsuperscript{1,2,‡}
\vskip 1em
\textsuperscript{1}\,Université de Montréal; \textsuperscript{2}\,Québec
Centre for Biodiversity Sciences; \textsuperscript{3}\,Molecular
Epidemiology and Public Health Laboratory, Hopkirk Research Institute,
Massey University, Palmerston North, New
Zealand; \textsuperscript{4}\,Paul G. Allen School for Global Health,
Washington State University, Pullman, WA, United
States; \textsuperscript{5}\,???\\
\textsuperscript{‡}\,These authors contributed equally to the work\\
\vskip 1em
\textbf{Correspondance to:}\\
Timothée Poisot --- \texttt{timothee.poisot@umontreal.ca}\\
}
\end{flushleft}
